\acknowledgments

My research career has been accompanied by the Covid-19 pandemic. I would never have completed this work without the help of many people.

First of all, I want to express my greatest appreciation for my supervisor, Professor WANG Yan, for his years of hands-on physical training, continuous advice, and kindly support. I have learned the beauty of understanding the ocean from a physical and discrete mathematical way, and known how to develop, organize, and express my ideas in sientific research. He also encourages me in many aspects of research and life. These skills and guidance are crucial for my later career development.

I thank the members of my thesis committee, Professor Julian Mak and Professor Li Jiying for their insightful comments to help me polish this work. 

I would like to thank my group members and colleagues in HKUST -- Mr. WEI Huaiyu, Ms. CHAI Xia, Mr. DENG Peng, Ms. ZHANG Ying, Mr. CHENG Weichong, Dr. LI Dou, Dr. XIE Chenyue, and Ms. QUAN Mingyu. I spent most of my colorful graduate life with them, learned most of the necessary academic skills from senior students, and got moral support from them.

I also want to thank my supervisor and the Department of Ocean Science (OCES) for providing me with a postgraduate scholarship and offering me such a precious opportunity to explore the mysteries of the world from the perspective of the physical oceanography. 

Last but not least, I thank my family members, for my parents' great support in mental and physical health. I wanted to share every moment of happiness and each stage of success with them.

\endacknowledgments
